Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of NIRCam Detectors

### 2018-08-24 ms.tex
wrote up some more on summarizing the ground-based tests.

Experience with the Hubble Space Telescope (HST), \spitzer, and \kepler\ shows that there many potential systematics that can affect high precision time series \citep[e.g.][]{beichman2014pasp}.
Many of these effects are detector-related including charge trapping on HST's detector \citep{berta2012flat_gj1214,zhou2017chargeTrap}, intra-pixel sensitivity on the short wavelength bands of \spitzer\ IRAC \citep{moralesCalderon2006LdwarfsWeatherIPC} and sensitivity to pointing jitter with \kepler\footnote{https://keplerscience.arc.nasa.gov/K2/Performance.shtml} \citep{beichman2014pasp}.

The NIRCam instrument \citep{rieke2005NIRCamSPIE} contains a slitless grism mode \citep{greene2017jatisNIRCam} that is analogous to the WFC3 grism mode on HST that has been successfully employed on many transiting planets \citep[e.g.]{deming13,kreidberg2014wasp43,sing2016continuum,wakeford2017hatp26}.
The grism mode will collect moderate resolution R$\sim$1100-1700 spectra and employ the long wavelength channel to cover the wavelength range 2.4 to 5.0~$\mu$m.
This grism mode can be used simultaneously with short wavelength weak lens imaging or the Dispersed Hartmann Sensor mode \citep{schlawin2017dhs}. If it becomes an approved and implemented mode, the DHS will permit spectroscopy from 1.0 to 2.0~$\mu$m and will work for very bright targets inaccessible by other modes.

@@

Known detector effects that could affect stability:
\begin{itemize}[noitemsep]
	\item Intrapixel sensitivity - including sub-pixel flat fielding issues, sub-pixel crosshatching on the detectors
	\item Asic-specific effects - pre-amp reset. 
\end{itemize}

The NIRCam detectors

@@

\begin{deluxetable*}{ccCrlc}[b!]
\tablecaption{Summary of Tests \label{tab:mathmode}}
\tablecolumns{7}
%\tablenum{2}
\tablewidth{0pt}
\tablehead{
\colhead{Name} &
\colhead{Location} &
\colhead{UT dates} &
\colhead{Best Stability} & 
\colhead{Light Source} & 
\colhead{Instrument Mode} \\
\colhead{} &
\colhead{} &
\colhead{(YYYY-mm-dd)} &
\colhead{(ppm)} &
\colhead{}
}
\startdata
CV 3       & NASA Goddard  & 2016       & 500   & LED           & WLP8 imaging \\
OTIS       & NASA Goddard  & 2017       &       & Continuum     & Grism spectroscopy \\
GL dewar   & Steward Obs.  & 2015-2016  &       & LED	        & flood-illuminated imaging \\
Asic dewar & Steward Obs.  & 2017-2019  &       & LED           & pinhole flood-illuminated imaging \\
\enddata
\tablecomments{Cryogenic vacuum (CV).}
\end{deluxetable*}

\section{Pre-amp Resets}
The NIRCam detectors' pre-amps are reset once per frame (as opposed to once per integration) to prevent large amplifier drifts over an integration \citep{robberto2014refPixPreAmp}

@@

\section{Extra Info}

>>>>

Experience with the Hubble Space Telescope (HST), \spitzer, and \kepler\ shows that there many potential systematics that can affect high precision time series and prevent photon-limited performance unless corrected for \citep[e.g.][]{beichman2014pasp}.
Many of these effects are detector-related including charge trapping on HST's detector \citep{berta2012flat_gj1214,zhou2017chargeTrap}, intra-pixel sensitivity on the short wavelength bands of \spitzer\ IRAC \citep{moralesCalderon2006LdwarfsWeatherIPC} and sensitivity to pointing jitter with \kepler\footnote{https://keplerscience.arc.nasa.gov/K2/Performance.shtml} \citep{beichman2014pasp}.

The NIRCam instrument \citep{rieke2005nircamSPIE} contains a slitless grism mode \citep{greene2017jatisNIRCam} that is analogous to the WFC3 grism mode on HST that has been successfully employed on many transiting planets \citep[e.g.]{deming13,kreidberg2014wasp43,sing2016continuum,wakeford2017hatp26}.
The grism mode will collect moderate resolution R$\sim$1100-1700 spectra and employ the long wavelength channel to cover the wavelength range 2.4 to 5.0~$\mu$m.
This grism mode can be used simultaneously with short wavelength weak lens imaging or the Dispersed Hartmann Sensor mode \citep{schlawin2017dhs}. If it becomes an approved and implemented mode, the DHS will permit spectroscopy from 1.0 to 2.0~$\mu$m and will work for very bright targets inaccessible by other modes.

@@

\subsection{Known Detector Effects}
Known detector effects that could affect stability include:
\begin{itemize}[noitemsep]
	\item Intrapixel sensitivity - including sub-pixel flat fielding issues and sub-pixel crosshatching on the detectors \citep{shapiro2018crosshatch}
	\item Pre-amp reset offsets (an Asic-related effect) The NIRCam detectors' pre-amps are reset once per frame (as opposed to once per integration) to prevent large amplifier drifts over an integration \citep{robberto2014refPixPreAmp}.
The resets cause discontinuities in the (bias?) level that can be seen on reference pixels.
The NIRCam grism subarrays include reference pixels to mitigate these pre-amp offsets.
	\item 1/f noise - this is a noise source where most of the noise power is concentrated as low frequencies. 1/f noise causes spatial correlations in the fast-read direction (along detector rows). It is highly correlated between amplifiers, suggesting that it is caused by a common reference voltage. 1/f noise is efficiently removed by reference pixels
	\item Even/odd offsets - alternating columns have different bias levels. Additionally, there are offsets between columns that can change from frame to frame, especially on NIRCam's LW detector
	\item kTC noise - a random process due to the unknown amount of charge stored at the reset voltage level
\end{itemize}

@@

Table \ref{tab:testSummary} shows a summary of the ground-based tests that were performed on NIRCam detectors.
The flight NIRCam detectors, controllers, electronics, optics and instrument hardware were used in the Cryogenic Vacuum Test 3 (CV3) as well as OTIS (Optical Telescope Element and Integrated Science).
The GL dewar experiments used flight detectors, but a different controller (Leach).
The Asic dewar located at Steward Observatory in Tucson, Arizona used a spare NIRCam detector, a spare asic controller and the flight software, but no flight optics.

\begin{deluxetable*}{ccCrlc}[b!]
\tablecaption{Summary of Ground-Based Tests}\label{tab:testSummary}
\tablecolumns{7}
%\tablenum{2}
\tablewidth{0pt}
\tablehead{
\colhead{Name} &
\colhead{Location} &
\colhead{UT dates} &
\colhead{Best Stability} & 
\colhead{Light Source} & 
\colhead{Instrument Mode} \\
\colhead{} &
\colhead{} &
\colhead{(YYYY-mm-dd)} &
\colhead{(ppm)} &
\colhead{}
}
\startdata
CV 3       & NASA Goddard  & 2016       & 500   & LED           & WLP8 imaging \\
OTIS       & NASA Goddard  & 2017       &       & Continuum     & Grism spectroscopy \\
GL dewar   & Steward Obs.  & 2015-2016  &       & LED	        & flood-illuminated imaging \\
Asic dewar & Steward Obs.  & 2017-2019  &       & LED           & pinhole flood-illuminated imaging \\
\enddata
\tablecomments{Cryogenic vacuum (CV).}
\end{deluxetable*}

@@

%\section{Extra Info}
